\ttitle

### 2013-11-11 Chapters/Chapter6/data_gathering.tex
Draft, sent to Anne
WIP
Cropped graphs

>>>>

\TODO{Use common data sets. The WISDM dataset is not usefull because it has no transitions, only very clear blocks of the same activities. Include a plot to illustrate the problem?}

\begin{figure}\label{fig:wisdm_excerpt}
\centering
  \includegraphics[width=1\textwidth]{./Figures/Chapter6/data_collection/wisdm_excerpt.eps}
  \caption[Jumping variance ratios]{Excerpt from the WISDM data set \cite{kwapisz2011activity}. First five activities for subject $33$ are displayed. Due to the discontinuous nature of the recordings, this data set can not be used for change detection.}
\end{figure}
